Competing Constructions for German Measure Phrases

### 2017-03-15 Latex/article.tex
some work on previous analyses

\usepackage[small]{dgruyter}
\usepackage{microtype}
\usepackage{enumerate}

\newcommand{\wrt}{w.\,r.\,t.\ }
\newcommand{\Wrt}{W.\,r.\,t.\ }

\newcommand{\eg}{e.\,g.,}
\newcommand{\Eg}{E.\,g.,}

\newcommand{\ie}{i.\,e.,}
\newcommand{\Ie}{I.\,e.,}

\newcommand{\CxMdn}{\ensuremath{\mathsf{Ms_{[DN]}}}}
\newcommand{\CxMn}{\ensuremath{\mathsf{Ms_{[N]}}}}
\newcommand{\CxMan}{\ensuremath{\mathsf{Ms_{[AN]}}}}

\newcommand{\Sub}[1]{\ensuremath{\mathrm{_{#1}}}}
\newcommand{\Sup}[1]{\ensuremath{\mathrm{^{#1}}}}
\newcommand{\Subsf}[1]{\ensuremath{\mathsf{_{#1}}}}
\newcommand{\Supsf}[1]{\ensuremath{\mathsf{^{#1}}}}

@@

As stated in Section~\ref{sec:cogocl}, I consider it essential not to disregard generalisations discovered in descriptive, generative or formal frameworks, even if the accompanying formulations do not fit into probabilistic settings.
This section therefore reviews some existing analyses of the OGC-NAC alternation or related issues, including generative approaches.

@@

>>>>

\usepackage[small]{dgruyter}
\usepackage{microtype}
\usepackage{enumerate}
\usepackage{bm}

\newcommand{\wrt}{w.\,r.\,t.\ }
\newcommand{\Wrt}{W.\,r.\,t.\ }
\newcommand{\eg}{e.\,g.,}
\newcommand{\Eg}{E.\,g.,}
\newcommand{\ie}{i.\,e.,}
\newcommand{\Ie}{I.\,e.,}
\newcommand{\Sub}[1]{\ensuremath{\mathrm{_{#1}}}}
\newcommand{\Sup}[1]{\ensuremath{\mathrm{^{#1}}}}
\newcommand{\Subsf}[1]{\ensuremath{\mathsf{_{#1}}}}
\newcommand{\Supsf}[1]{\ensuremath{\mathsf{^{#1}}}}

@@

As stated in Section~\ref{sec:cogocl}, I consider it essential not to disregard generalisations discovered in descriptive, generative or formal frameworks, even if the accompanying formulations do not fit into probabilistic settings.
This section therefore reviews some existing analyses of the PGC-NAC alternation or related issues, including generative approaches.

@@

\begin{equation}
  \begin{split}
    Pr(y_i=1)       & = logit^{-1}(\pmb{\beta}\mathbf{X_i} + \alpha^{\text{measurelemma}}_{j_i} + \alpha^{\text{kindlemma}}_{k_i}) \\
    \text{where}\ \ & \mathbf{X_i}\ \text{is a vector of values for Badness, Genitives, } \\
                    & \text{Matchlength, Measureabbreviated, Measurecase,} \\
                    & \text{Measeurenumber, Minus1pos for}\ i \\
    \text{and}\ \   & \pmb{\beta}\ \text{a corresponding coefficient vector} \\
    \text{and}\ \   & \alpha^{\text{measurelemma}}_{j_i}\sim\mathcal{N}(\mu_j,\sigma_1) \\
    \text{and}\ \   & \alpha^{\text{kindlemma}}_{k_i}\sim\mathcal{N}(\mu_k,\sigma_2) \\
    \text{with}\ \  & \mu_1 \\
  \end{split}
  \label{eq:model:mnglmm}
\end{equation}
